Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-09 analysis/paper/paper.Rmd
Edits to closing

>>>>

Without the data underlying the paper, we as a community cannot adequately evaluate the work as it is presented.
Without the code that was used to analyse the data, we as a community cannot adequately evaluate the work as it is presented.
That is, while we may be standing on the shoulders of giants doing our work, we cannot see where they've been to do our work, which hinders our efforts.
